---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cocosoR

<!-- badges: start -->
<!-- badges: end -->

This program is an implementation of the Combined Compromise Solution (CoCoSo) Method (A combined compromise solution (CoCoSo) method for multi-criteria decision-making problems, Yazdani, M., Zarate, P., Kazimieras Zavadskas, E., & Turskis, Z. (2019), <https://doi.org/10.1108/MD-05-2017-0458> ) based on an integrated simple additive weighting and compromise exponentially weighted product model.

## Installation

You can install the development version of cocosoR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sergiofloquet/cocosoR")
```

```{r example}
library(cocosoR)
```


## CoCoSo Method

This package is an implementation of the Combined Compromise Solution (CoCoSo) Method [1] based on an integrated simple additive weighting and compromise exponentially weighted product model. We can use the data from [1] as example:


```{r, include=T, message = FALSE, warning = FALSE}
data(example_cocoso)
example_cocoso
```

CoCoSo method can be apply making the final ranking of all alternatives. 

```{r, include=T, message = FALSE, warning = FALSE}
result<- cocoso(example_cocoso)
result
```


In addition we present in results all three aggregation strategies and the sum and product weight, used in [1].



## References:

[1] Yazdani, M., Zarate, P., Kazimieras Zavadskas, E., & Turskis, Z. (2019). A combined compromise solution (CoCoSo) method for multi-criteria decision-making problems. Management Decision, 57(9), 2501-2519.

