---
title: "Introduction to CoCoSo Method"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to CoCoSo Method}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(rmarkdown) ; library(knitr)
```

```{r setup}
library(cocosoR)
```

## CoCoSo Method

This package is an implementation of the Combined Compromise Solution (CoCoSo) Method [1] based on an integrated simple additive weighting and compromise exponentially weighted product model. We can use the data from [1] as example:


```{r, include=T, message = FALSE, warning = FALSE}
data(example_cocoso)
paged_table(example_cocoso, options = list(rows.print = 10, rownames.print = FALSE) ) 
```

CoCoSo method can be apply making the final ranking of all alternatives. 

```{r, include=T, message = FALSE, warning = FALSE}

result<- cocoso(example_cocoso)
paged_table(result, options = list(rows.print = 10, rownames.print = FALSE) ) 
```


In addition we present in results all three aggregation strategies and the sum and product weight, used in [1].




## References:

[1] Yazdani, M., Zarate, P., Kazimieras Zavadskas, E., & Turskis, Z. (2019). A combined compromise solution (CoCoSo) method for multi-criteria decision-making problems. Management Decision, 57(9), 2501-2519.
